---
title: "Titanic Analysis Exercise"
author: "Lyttia Cancinos-McManus"
date: "July 16, 2018"
output: html_document
---
# Titanic Analysis Exercise

*#0 - Install and load packages and data. Data file can be saved to local machine from this repo [here](https://github.com/Lyttia/Data_Analysis_Exercises/blob/master/titanic_train.rda). Replace data file address in the `load()` function to local address.*

```{r}
install.packages("ggplot2")
install.packages("dplyr")
library("dplyr")
library("ggplot2")
load("C:/Users/lytti/Desktop/Datasets/titanic_train.rda")
```

*#1 - Check the structure of `titanic_train`. Clean data for proper use with DataCamp exercises.*

```{r}
str(titanic_train)
titanic <- select(titanic_train, Survived, Pclass, Sex, Age)
str(titanic)
```

*#2 - Use `ggplot()` to explore data. I plotted the distribution of sexes within the classes of the ship.*

```{r}
ggplot(titanic, aes(x = Pclass, fill = Sex)) +
  geom_bar(position = "dodge")
```

*#3 - These bar plots won't help me estimate my chances of survival. Plot 2: add `facet_grid()` layer: `. ~ Survived`*

```{r}
ggplot(titanic, aes(x = Pclass, fill = Sex)) +
  geom_bar(position = "dodge") +
  facet_grid(. ~ Survived)
```

*#4 - Define an object for `position_jitterdodge`, to use below*

```{r}
posn.jd <- position_jitterdodge(0.5, 0, 0.6)
```

*#5 - Plot 3: Include `Age` on `y`, use the position object from above, `geom_point`, `Sex` mapped to `color`*

```{r}
ggplot(titanic, aes(x = Pclass, y = Age, color = Sex)) +
  geom_point(position = posn.jd, size = 3, alpha = 0.5) +
  facet_grid(. ~ Survived)
```
